### 2014-07-04 manuscript/manuscript.tex

>>>>

\section*{Supplementary Table Legends}

{\bf Table S1:} Species names, genome accessions, RNA-seq data
sources, Pubmed IDs, sequencing platform and notes for each dataset
used for this study.

{\bf Table S2:} The Pfam, Rfam and RUF identifiers for each entry
corresponding to Figure~\ref{fig:1}.

{\bf Table S3:} Quality control measures computed for each RNA-seq
dataset used in this study. The values are defined in detail in the
Methods section.
